Type-Safe Modular Parsing

### 2017-01-10 paper/sections/RelatedWork.tex
Mention some future work in conclusion.

\paragraph{Extensible Parsing Algorithms}
Extensible parsing algorithms are another area that indeed relates to
separate compilation. Specifically, \cite{Bravenboer2009} introduces
\textit{parse table composition}, where grammars are compiled
to the generation of parse tables. Those parse tables are expressed as DFAs or NFAs, later they
can be composed by an algorithm, so as to provide separate compilation
for parsing. Nevertheless, the generation of parse tables is rather
expensive in terms of performance.
Furthermore, our approach supports \emph{both} separate compilation
as well as \emph{modular type-checking}. The extensibility of
parsing is further available at language composition
and lexical level.
%\haoyuan{we do not have explicit
%  correspondence/relationship between abstract syntax and the parser.}

@@

Some more recent papers~\cite{Ford2002,Might2011,Frost2008} proposed a series of
novel parsing techniques that addressed the issue
of left-recursion. We have selected Packrat
Parsing for our prototype implementation, as the combinators are
convenient to use in Scala, which is a platform where functional
laziness and Object Algebras can perfectly coexist. Also, its support
for direct left-recursion is already helpful for designing real-world
parsers practically, though~\cite{warth2008} further demonstrated that
general left-recursion is supported theoretically.
Yet we have mentioned that the components used in our approach
can have alternatives to achieve better modular parsing.

\paragraph{Extensibility} To the best of our knowledge, none of the existing techniques
address the problem of producing extensible ASTs. Certainly, there has been a lot of work on extensible
data types, in both functional and object-oriented programming.
For instance, the famous DTC paper~\cite{swierstra2008} represents
modular ASTs using co-products of every two functors, which forms a
binary tree structure. Later
Oliveira et al. presented MRM~\cite{Oliveira2015} in Haskell, which is
similar to DTC but adopts a list of functors in type-level lists
instead. Other related work
includes~\cite{Bahr2014}, where data types are flexible with
composition as well as decomposition.

>>>>

\paragraph{Extensible Parsing Algorithms}
Extensible parsing algorithms are another area that indeed relates to
separate compilation. Specifically, \cite{Bravenboer2009} introduces
\textit{parse table composition}, where grammars are compiled
to the generation of parse tables. Those parse tables are expressed as DFAs or NFAs, later they
can be composed by an algorithm, so as to provide separate compilation
for parsing. Nevertheless, the generation of parse tables is rather
expensive in terms of performance.
Furthermore, our approach supports both \emph{separate compilation}
as well as \emph{modular type-checking}. The extensibility of
parsing is further available at language composition
and lexical level.
%\haoyuan{we do not have explicit
%  correspondence/relationship between abstract syntax and the parser.}

@@

Some more recent papers~\cite{Ford2002,Might2011,Frost2008} proposed a series of
novel parsing techniques that addressed the issue
of left-recursion. We have selected Packrat
Parsing for our prototype implementation, as the combinators are
convenient to use in Scala, and Object Algebras can be naturally realized with
OO inheritance. Also, its support
for direct left-recursion is already helpful for designing real-world
parsers practically, though~\cite{warth2008} further demonstrated that
general left-recursion is supported theoretically.
Yet we have mentioned that the components used in our approach
can have alternatives to achieve better modular parsing.

\paragraph{Extensibility} To the best of our knowledge, none of the existing parsing techniques
address the problem of producing extensible ASTs. Certainly, there has been a lot of work on extensible
data types, in both functional and object-oriented programming.
For instance, the famous DTC paper~\cite{swierstra2008} represents
modular ASTs using co-products of every two functors, which forms a
binary tree structure. Later
Oliveira et al. presented MRM~\cite{Oliveira2015} in Haskell, which is
similar to DTC but adopts a list of functors in type-level lists
instead. Other related work
includes~\cite{Bahr2014}, where data types are flexible with
composition as well as decomposition.
